Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-05-19 Markdown Documents/Manuscript.Rmd
Plots

---
title: Estimating the Financial Impact of Wildfire Smoke on US National parks
author:
- affiliation: Boise State University - Human Environment Systems
  name: Matt Clark
- affiliation: University of Michigan
  name: Alexander Killion
- affiliation: Boise State University
  name: Matthew A. Williamson
- affiliation: Boise State University
  name: Vicken?
- affiliation: Boise State University
  name: Laura? (undergrad who will continue working over summer)
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    template: /Users/Matthewclark989/Documents/LatexPractice/templatedocs/svm_ms_template.tex
fontfamily: mathpazo
fontsize: 11pt
geometry: margin=1in
keywords: pandoc, r markdown, knitr
bibliography: /Users/Matthewclark989/Documents/SmokeProject/References.bib
thanks: If we want to thank anyone? Maybe Moji?.
abstract: National Parks are important. National Parks are low on funding which affects their ability to do their job. A key way they get this funding is through visitation. Wildfire smoke affects visitation greatly and is out of ther control. Wildfires are expected to increase in the Pacific West and Intermountain regions. Over the last 38 years, we estimate that wildfire smoke has led to a 12% overall visitation decrease to National Parks in these regions. When accounting for visitation fees, this loss may have cost the National Park Service as much as $580 million in total. Wildfires and the smoke it produces is supposed to increase over the next 50 years. Assuming a linear trend in smoke, visitation overall, and park fees, we might see a financial loss to the park service of $XX. Our recomendation is that....NPS work with the forest service to prevent fires in areas close to parks?? Do they already do that??    
---
# 1. Introduction

@@

### 2.2.3. Smoke, Fee, & Visitation Projections

@@

x$r2<-round(x$Correlation^2,digits=2)
x$Correlation<-round(x$Correlation,digits=2)
names(x)<-c("Model","Time Period", "Correlation", "R^2")
formattable::formattable(x)
```
## 3.4. Future Projections

>>>>

---
title: Estimating the Financial Impact of Wildfire Smoke on US National parks
author:
- affiliation: Boise State University - Human Environment Systems
  name: Matt Clark
- affiliation: University of Michigan
  name: Alexander Killion
- affiliation: Boise State University
  name: Matthew A. Williamson
- affiliation: Boise State University
  name: Vicken?
- affiliation: Boise State University
  name: Laura? (undergrad who will continue working over summer)
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    template: /Users/Matthewclark989/Documents/LatexPractice/templatedocs/svm_ms_template.tex
fontfamily: mathpazo
fontsize: 11pt
geometry: margin=1in
keywords: pandoc, r markdown, knitr
bibliography: /Users/Matthewclark989/Documents/SmokeProject/References.bib
thanks: If we want to thank anyone? Maybe Moji?.
abstract: National Parks are important. National Parks are low on funding which affects their ability to do their job. A key way they get this funding is through visitation. Wildfire smoke affects visitation greatly and is out of ther control. Wildfires are expected to increase in the Pacific West and Intermountain regions. Over the last 38 years, we estimate that wildfire smoke has led to a 12% overall visitation decrease to National Parks in these regions. When accounting for visitation fees, this loss may have cost the National Park Service as much as $580 million in total. Wildfires and the smoke it produces is supposed to increase over the next 50 years. Assuming a linear trend in smoke, visitation overall, and park fees, we expect to see significant financial losses to the National Park Service. Our recomendation is that....NPS work with the forest service to prevent fires in areas close to parks?? Do they already do that??    
---
# 1. Introduction

@@

@@

x$r2<-round(x$Correlation^2,digits=2)
x$Correlation<-round(x$Correlation,digits=2)
names(x)<-c("Model","Time Period", "Correlation", "R^2")
formattable::formattable(x)
```
